\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-09-04 journalWallFriction/simulation.tex
updated reachable plots and paper

\section{Two Optimal Results}\label{sec:optimalResults}
  Algorithm ??? provided a technique to bring two particles to goal positions using global inputs, but did not optimize path length.  
  In this section we present two results that can be incorporated into Algorithms ??? and ??? to generate shorter motion paths.

 \subsection{Example: Shortest Path in a Square Workspace}\label{subsec:square}
 Changing the relative positions of particles in any workspace requires making one particle contact the boundary.
 If the goal configuration cannot be reached in one move but can be reached in three moves, the shortest path has a simple solution. The first move, $m_1$, makes one particle contact a wall, $m_2$ adjusts the relative spacing error  to zero, and $m_3$ takes the particles to their final positions. 
$m_2$ cannot be shortened, so optimization depends on choosing the location where the particle contacts the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal contact location, as shown in Fig. \ref{fig:reflection}. 
  There are four walls, and four candidate solutions, but some candidate solutions may be invalid because a different boundary is hit before the desired first contact position in move $m_1$ (light grey regions) or  invalid because $m_2$ cannot generate the goal relative spacing (dark grey regions).
 %
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{Reflection.pdf}\end{overpic}
\vspace{-2em}
\caption{\label{fig:reflection}
\textcolor{red}{add 0.2 increments to both, add green dot on left image, draw incident and reflected angle}
The shortest three-move path that reconfigures two particles has the property that the incident angle equals the reflected angle, as shown at left. (right) The first contact is colored red if the red particle is the first to touch a boundary, and colored blue if the blue particle is the first to touch.
} \vspace{-1em}
\end{figure}
%

>>>>

\section{Two Optimal Results}\label{sec:optimalResults}
  Algorithm \ref{alg:optimalAlg} provided a technique to bring two particles to goal positions using global inputs, but did not optimize path length.  
  In this section we present two results that can be incorporated into Algorithms \ref{alg:polygonReachbale} and \ref{alg:circularReachbale} to generate shorter motion paths.

 \subsection{Example: Shortest Path in a Square Workspace}\label{subsec:square}
 Changing the relative positions of particles in any workspace requires making one particle contact the boundary.
 If the goal configuration cannot be reached in one move but can be reached in three moves, the shortest path has a simple solution. The first move, $m_1$, makes one particle contact a wall, $m_2$ adjusts the relative spacing error  to zero, and $m_3$ takes the particles to their final ositions. 
$m_2$ cannot be shortened, so optimization depends on choosing the location where the particle contacts the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal contact location, as shown in Fig. \ref{fig:reflection}. 
  There are four walls, and four candidate solutions, but some candidate solutions may be invalid because a different boundary is hit before the desired first contact position in move $m_1$ (light grey regions) or  invalid because $m_2$ cannot generate the goal relative spacing (dark grey regions).
 %
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{Reflection.pdf}\end{overpic}
\vspace{-2em}
\caption{\label{fig:reflection}
\textcolor{red}{add 0.2 increments to both, add green dot on left image, draw incident and reflected angle}
The shortest three-move path that reconfigures two particles has the property that the incident angle equals the reflected angle, as shown at left. (right) The first contact is colored red if the red particle is the first to touch a boundary, and colored blue if the blue particle is the first to touch.
} \vspace{-1em}
\end{figure}
%

### 2018-09-04 journalWallFriction/theory2robAlgs.tex
updated reachable plots and paper

The $\Delta$ configuration makes it easy to compute the accessible workspace.  Due to symmetry of the workspace, the fraction of the $\Delta$ configuration space reachabable in $2 k$ moves is a function of only the initial separation distance $d_{12}$.

@@

@@

>>>>

The $\Delta$ configuration makes it easy to compute the accessible workspace.  
 Due to symmetry of the workspace, the fraction of the $\Delta$ configuration space reachable in $2 k$ moves is a function of only the initial separation distance $d_{12}$.
 The angle $\theta$ between the initial particle positions simply rotates the reachable $\Delta$ configuration space.

@@

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{reachableSetsFuncDistance}\end{overpic}
\caption{\label{fig:reachableSetsFuncDistance}
  Reachable fraction of  $\Delta$ configuration space  as a function of initial distance $d_{12}$.  
  As long as the initial configurations are distinct, the reachable set grows quickly. 
   Only epipolar locations are unreachable, but can be asymptotically reached.
}
\end{figure}

@@

\begin{figure}
\centering
\begin{overpic}[width=.8\columnwidth]{ReachableSets0p1}\end{overpic}
\begin{overpic}[width=.8\columnwidth]{ReachableSets0p3}\end{overpic}
\caption{\label{fig:reachableSets}
  Plots showing the 2, 4, 6, 8, 10, 12, and 14-move reachable sets in the  $\Delta$ configuration space for  $d_{12} = 0.1$ and $0.3$.  
  Shown are reachable sets with initial particle-to-particle angle $\theta=0$, all other sets for other angle values can be formed by rotating by $\theta$.
}
\end{figure}
